# Working with glycoMusubi in R {#r-workflow}

This chapter provides practical R workflows for loading, querying, analysing, and visualising glycoMusubi. All examples assume that the Parquet files have been generated by running the ETL pipeline and are available in the `kg/` directory. The same Parquet files that power the Shiny application support custom analyses, network exploration, and publication-quality figures, making R an effective environment for both interactive exploration and reproducible research with the knowledge graph.

## Prerequisites and loading the knowledge graph

Before working with the knowledge graph, several R packages are required. The `arrow` package provides high-performance Parquet reading, `dplyr` and `tidyr` handle data manipulation, `igraph` enables network analysis, `visNetwork` produces interactive graph visualisations, and `ggplot2` generates static plots.

```{r install-deps, eval=FALSE}
install.packages(c("arrow", "dplyr", "tidyr", "igraph",
                    "visNetwork", "ggplot2", "DT"))
if (!requireNamespace("BiocManager", quietly = TRUE))
  install.packages("BiocManager")
BiocManager::install("ComplexHeatmap")
```

Loading the knowledge graph is straightforward. The two core data frames -- nodes and edges -- contain all entities and relationships. Each node carries an identifier, a human-readable name, a type label (such as protein, glycan, enzyme, disease, compound, or site), and the source database from which it was curated. Edges connect source and target nodes through typed relations.

```{r load-kg, eval=FALSE}
library(arrow)
library(dplyr)

nodes <- read_parquet("../../kg/nodes.parquet")
edges <- read_parquet("../../kg/edges.parquet")
cat("Nodes:", nrow(nodes), "| Edges:", nrow(edges), "\n")
```

The key columns are `id`, `source`, and `target` for entity identifiers (e.g., `P02768` for a UniProt protein or `G00055MO` for a GlyTouCan glycan), `node_type` and `relation` for category labels, `name` for human-readable labels, and `source_db` for provenance tracking back to the originating database.

## Basic queries

The simplest queries retrieve immediate neighbours of a given entity. To find all glycans associated with a protein, filter the edges for `has_glycan` relations originating from the protein of interest and join with the nodes table to obtain human-readable names. The same pattern applies when looking up enzymes that catalyse the biosynthesis of a particular glycan -- filter edges where the target matches the glycan identifier and the relation is `catalyzes`, then join for names.

```{r query-glycans, eval=FALSE}
protein_id <- "P02768"
glycans <- edges %>%
  filter(source == protein_id, relation == "has_glycan") %>%
  inner_join(nodes, by = c("target" = "id")) %>%
  select(glycan_id = target, glycan_name = name, source_db)
glycans
```

```{r query-enzymes, eval=FALSE}
glycan_id <- "G00055MO"
enzymes <- edges %>%
  filter(target == glycan_id, relation == "catalyzes") %>%
  inner_join(nodes, by = c("source" = "id")) %>%
  select(enzyme_id = source, enzyme_name = name)
enzymes
```

Multi-hop queries chain these single-hop lookups to traverse longer paths through the knowledge graph. For example, to discover diseases associated with a particular glycan, first find the proteins that carry that glycan, then find the diseases associated with those proteins. This two-hop traversal follows the path glycan to protein to disease and can reveal indirect relationships not apparent from examining any single database.

```{r multi-hop, eval=FALSE}
glycan_id <- "G00055MO"
proteins <- edges %>%
  filter(target == glycan_id, relation == "has_glycan") %>%
  pull(source)
diseases <- edges %>%
  filter(source %in% proteins, relation == "associated_with_disease") %>%
  inner_join(nodes, by = c("target" = "id")) %>%
  select(protein = source, disease_name = name) %>%
  distinct()
diseases
```

## Network analysis with igraph

For graph-theoretic analyses, glycoMusubi can be loaded directly into an igraph object. The `graph_from_data_frame` function accepts the edges and nodes data frames, producing a directed graph on which standard network metrics -- degree distribution, connected components, shortest paths, and centrality measures -- can be computed.

```{r igraph-build, eval=FALSE}
library(igraph)
g <- graph_from_data_frame(
  d = edges %>% select(from = source, to = target, relation),
  directed = TRUE,
  vertices = nodes %>% select(name = id, node_type)
)
cat("Vertices:", vcount(g), "| Edges:", ecount(g), "\n")
```

The degree distribution of glycoMusubi follows a heavy-tailed pattern typical of biological knowledge graphs, with most entities having few connections and a small number of hub nodes -- highly studied proteins, common glycans -- accumulating many edges. This structure has practical implications for querying: hub nodes will appear frequently in multi-hop paths, so filtering by relation type before joining is essential for performance.

```{r degree-dist, eval=FALSE}
library(ggplot2)
deg_df <- data.frame(degree = degree(g, mode = "all"))
ggplot(deg_df, aes(x = degree)) +
  geom_histogram(bins = 100, fill = "steelblue", colour = "white") +
  scale_x_log10() + scale_y_log10() +
  labs(title = "glycoMusubi Degree Distribution",
       x = "Degree (log)", y = "Count (log)") +
  theme_minimal()
```

Connected component analysis reveals whether the graph forms a single connected body or fragments into isolated subgraphs. Shortest path queries can trace the connections between seemingly unrelated entities, such as a small molecule and a disease phenotype, revealing the biological intermediaries that link them.

```{r components-paths, eval=FALSE}
comp <- components(g, mode = "weak")
cat("Components:", comp$no, "| Largest:", max(comp$csize), "\n")

sp <- shortest_paths(g, from = "CHEMBL25", to = "Breast cancer",
                     output = "vpath")
if (length(sp$vpath[[1]]) > 0)
  cat("Path:", paste(names(sp$vpath[[1]]), collapse = " -> "), "\n")
```

## Subgraph extraction and external data integration

For focused analyses, extracting a local subgraph around an entity of interest is often more practical than working with the full graph. A two-hop subgraph captures the immediate neighbourhood and its neighbours, providing sufficient context for most protein-centric investigations while keeping the data manageable.

```{r subgraph, eval=FALSE}
protein_id <- "Q9Y2C3"
hop1 <- edges %>% filter(source == protein_id | target == protein_id)
nbr_ids <- unique(c(hop1$source, hop1$target))
hop2 <- edges %>% filter(source %in% nbr_ids | target %in% nbr_ids)
sub_nodes <- nodes %>%
  filter(id %in% unique(c(hop2$source, hop2$target)))
cat("Subgraph:", nrow(sub_nodes), "nodes,", nrow(hop2), "edges\n")
```

One of the strengths of working with glycoMusubi in R is the ease of joining external datasets. For instance, single-cell expression data from the Tabula Sapiens atlas can be joined to enzyme nodes to enrich the graph with transcriptomic context. By computing summary statistics such as mean expression and coefficient of variation per gene, one can identify which enzymes in the knowledge graph show the most cell-type-specific expression patterns.

```{r join-expression, eval=FALSE}
library(tidyr)
expr <- read_parquet("../../data_clean/tabula_sapiens_enzyme_expr.parquet")
mean_expr <- expr %>%
  pivot_longer(-cell_type, names_to = "gene", values_to = "expr") %>%
  group_by(gene) %>%
  summarise(mean_expr = mean(expr), cv = sd(expr) / mean(expr))
enzyme_nodes <- nodes %>% filter(node_type == "enzyme")
enriched <- enzyme_nodes %>%
  inner_join(mean_expr, by = c("name" = "gene"))
head(enriched)
```

## Interactive visualisation with visNetwork

The visNetwork package renders interactive, explorable graph visualisations directly in RStudio or a web browser. By mapping node types to colours and edge relations to labels, the resulting visualisation provides an intuitive interface for navigating the knowledge graph. Proteins appear in blue, glycans in green, enzymes in orange, diseases in red, compounds in purple, and sites in teal, creating a visual language that makes relationship patterns immediately apparent.

```{r visnetwork, eval=FALSE}
library(visNetwork)
vis_nodes <- sub_nodes %>%
  transmute(id = id,
            label = ifelse(nchar(name) > 20, substr(name, 1, 17), name),
            group = node_type,
            title = paste0("<b>", name, "</b><br>", node_type))
vis_edges <- hop2 %>%
  transmute(from = source, to = target, label = relation, arrows = "to")
visNetwork(vis_nodes, vis_edges, width = "100%", height = "600px") %>%
  visGroups(groupname = "protein",  color = "#4A90D9") %>%
  visGroups(groupname = "glycan",   color = "#7ED321") %>%
  visGroups(groupname = "enzyme",   color = "#F5A623") %>%
  visGroups(groupname = "disease",  color = "#D0021B") %>%
  visGroups(groupname = "compound", color = "#9013FE") %>%
  visGroups(groupname = "site",     color = "#50E3C2") %>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE) %>%
  visLayout(randomSeed = 42)
```

## Integration with the Shiny app

The Shiny application at `localhost:3838` reads the same Parquet files used in these R workflows. Any query performed through the Shiny interface can be replicated programmatically, which is useful for building reproducible analysis pipelines or extending the exploration beyond what the app's UI supports. The following helper function demonstrates how to extract all relationships for a given protein, mirroring the Shiny app's protein exploration panel.

```{r shiny-equiv, eval=FALSE}
explore_protein <- function(pid, kg_dir = "../../kg") {
  n <- read_parquet(file.path(kg_dir, "nodes.parquet"))
  e <- read_parquet(file.path(kg_dir, "edges.parquet"))
  info <- n %>% filter(id == pid)
  rels <- e %>% filter(source == pid | target == pid) %>%
    left_join(n, by = c("target" = "id")) %>%
    select(relation, related_id = target, related_name = name, node_type)
  list(protein = info, relationships = rels)
}
explore_protein("P02768")$relationships %>% count(relation)
```

## Summary

This chapter demonstrated the full R workflow for glycoMusubi, from loading the Parquet files through basic queries, multi-hop traversals, network analysis with igraph, external data integration, and interactive visualisation with visNetwork. The consistent use of Parquet as the storage format ensures that the same data powering the Shiny app is directly accessible for custom analyses, enabling researchers to move fluidly between interactive exploration and programmatic investigation.
